\documentclass[14pt]{article}

\title{InfoSec2015 Keynotes Summary}
\date{\today}
\author{Igor Pevtsov, 53501/3}
 
\begin{document}
  	\maketitle

	\section{The Science, Engineering and Business of Cyber Security (Keynote1 css`13) summary}
	\begin{itemize}
	\item In modern world status of Computer Science is ambiguos, it belongs to several Colleges simultaneously.
	\item The large-scale adoption of internet services across diverse global populations is one indicator that the average consumer is reasonably comfortable with the collateral risks.
	\item US Department of Defence recognized cyberspace as a man-made domain within which wars will be conducted.
	\end{itemize}

	\section{The Cyber Arms Race (Keynote2 css`13) summary}
	\begin{itemize}
	\item 20-30 years before, desicion makers did not  see the Internet as something important, but today the situation is different: they realize how it can be useful in doing surveillance on citizens.
	\item The US NSA program called PRISM is one of the most powerful instruments for surveillance and monitoring people all over the world
	\item USA has the exceptional opportunities for monitoring hundreds millions of people because all of the most popular internet services are located in the USA (Google, Facebook, Twitter, etc.).
	\item Information leaking is possible everywhere, even in the Intelligence Agencies.
	\end{itemize}

	\section{Exciting Security Research Opportunity: Next-generation Internet (Keynote1 css`14) summary}
	\begin{itemize}
	\item The success of the Internet has created a dependency on communication as many of the processes underpinning the foundations of modern society would grind to a halt should communication become unavailable.
	\item Important challenge is how to scale authentication of entities (e.g., AS ownership for routing, name servers for DNS, or domains for TLS) to a global environment.
	\item The design of a next-generation Internet, that is secure, available, and offers privacy by design; that provides appropriate incentives for a transition to the new architecture; and that considers economic and policy issues at the design stage, is being studied.
	\end{itemize}
\end{document}
